Tor's Usability for Censorship Circumvention

### 2015-12-10 paper/circumvention-experiment.tex
future work

\section{Results}

@@

We plan to finish the user study by the end of the semester. 
From this experiment, we hope to accomplish the following:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item {\bfseries Test an improved configuration interface} With the measurements collected
from testing the interface as-is, we will design and test improvements to minimize
time taken, paths taken, and error states reached.
\item {\bfseries Push changes} We have the support of Tor developers
to improve this interface. Additionally, since the configuration interface does not require 
any changes to the Tor Browser functionality, improvements to the interface will
be easy to deploy. 
\end{itemize}

>>>>

\section{Initial Results}

@@

The work summarized in the paper is only a part of the process of improving the Tor configuration
dialog for more usable censorship circumvention. We plan to continue this work by:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item {\bfseries Testing our design with a small-scale qualitative study.} It is critical to get in-depth data user train of thought as they user the interface, one-on-one interviews, and open-ended feedback. For this reason, we plan to run a small-scale qualitative study similar to the one we have run for the old interface. We plan to run these studies at the start of Spring 2015. 
\item {\bfseries Testing our design with a large-scale quantitative study.} To test our design alongside the old interface, we will recruit a large number of participants to try out both designs. The purpose of this is to get statistically significant results on whether our design choices have helped or not helped a user to configure successfully. We plan to run these studies at the start of Spring 2015.
\item {\bfseries Analyzing which design changes have made a positive impact.} We plan to instrument our interfaces to capture all clicks, window transitions, and other events so that we can analyze if our designs have helped our users connect faster and or with less effort. 
\item {\bfseries Push some changes.} We have the input and support of Tor developers
to improve this interface. Any improvements will be incorporated into the Tor Browser.
\end{itemize}

\noindent {\bfseries Quantitative experiment analyses} We want to show a statistically significant improvement in user effort for a successful connection. We have deemed this can be measured with various factors such as time, clicks, etc. For this reason, we will specifically be collecting data about: the total number of participants who have successfully circumvented censorship, the number of connection attempts for a successful connection, how much time participants spent configuring before a successful connection, the number of windows traversed in the UI, the number of clicks made, if bridge and proxy configuration interfered with each other, and how many people try repeat configuration settings.

One exciting analysis we will perform is to build a Markov model of the UI flow chart (like the one seen in Figure \ref{fig:interface}). We believe that this will be helpful in communicating participant behavior in aggregate since it will show the change in the UI flow structure, as well as how participants decisions have changed (e.g., in the old interface, a participant in a censorship environment which does not block Tor has a 0.4 chance of choosing ``connect,'' whereas in the new interface, the probability is 0.6). We have other visualizations in mind, such as displaying the number of windows traversed by each participant as a bar graph.\\

\noindent {\bfseries Deciding which design choices to incorporate} We have discussed how we will decide if a design change is beneficial enough to incorporate. Intuitively, changes which lead to higher success rates, faster time to completion, less clicking, less window traversal, and positive changes in behavior will be incorporated. If they have the converse of these effects, those changes will not be incorporated. However, when changes do result in a statistically significant improvement or challenge, we have chosen to incorporate changes if they provide cohesion with other changes which do have positive effects. If changes seem to be uncorrelated to positive effects and do not show statistical significance, we will not incorporate those changes. \\

\noindent {\bfseries Looking Forward} We will help incorporate changes into the Tor browser. Since we have developer support, it is not expected that we implement our changes, but we will advise them on any changes that they make. We hope that our work is able to help people more easily access the free Internet.
